TODO: title

### 2014-05-05 paper/main.tex
prepped for re-re-re-run

  % evaluation and code to run these algortihms available at.
  % citations and lenskit info

  Both nearest neighbor algorithms, User-User and Item-Item subtract the UserItemBaseline score from the ratings before performing similarity calcuations
  %TODO: verify this claim.

  Each algorithm was configured and tuned similarly to Ekstrand's 2012 lenskit evaluation \cite{ekstrand2012recommenders}.
%%%%%%%%%%%%%%%%%%%%%%
  Since this evaluation was on a slightly different dataset (MovieLens 10M), we performed only minor tuning from these parameters.
  Most notably we found the tuning of the damping parameter used in the baseline recommenders to be too large for this dataset.
  As the damping can have a large effect on baseline quality for new users, we adjusted to a more reasonable damping for this dataset.
  Overall, we did not find our results to be highly sensitive to minor tuning changes, although specific values may change slightly.
%%%%%%%%%%%%%%%%%%%%%%

>>>>

  %TODO: verify these claims.
  %TODO: check for examples of how to write this
  % algorithm is configured as such.
  %TODO: topic sentence.

  % evaluation and code to run these algortihms available at.
  % citations and lenskit info
  Each algorithm was configured and tuned similarly to Ekstrand's 2012 lenskit based evaluation \cite{ekstrand2012recommenders}.
%%%%%%%%%%%%%%%%%%%%%%
  Since this evaluation was on a slightly different dataset (MovieLens 10M), we performed only minor tuning from these parameters.
  Most notably we found the tuning of the damping parameter used in the baseline recommenders to be too large for this dataset.
  As the damping can have a large effect on baseline quality for new users, we adjusted to a more reasonable damping for this dataset.
  Overall, we did not find our results to be highly sensitive to minor tuning changes, although specific values may change slightly.
%%%%%%%%%%%%%%%%%%%%%%
